### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
nearly finish with todos from todo.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Precursor Solutions}
\label{sec:exp-sol}
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aqueous solution).
The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl alcohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-\gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimization} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
\ds{
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied. %to create a valley in between. 
This allowed material to only be deposited on the area between the tape.
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} speed was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization of \ch{ZrO2} layers}
All characterization procedures were executed at room temperature.
\iffalse
%All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
%\td{5kV, raum temperature, vacuum???}
%
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). 
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
For transmittance the light entered the sample from the side with the layer. 
The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
%\td{
%
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
%. (where are the conditions?)}
All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
\fi

@@

The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the ZrO2 layer.

@@

Another measure is the density of shorted elements $\rho$ (pinhole density), calculated in following way:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e.\ my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Production of Precursor Solutions}
\label{sec:exp-sol}
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aqueous solution).
The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl alcohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-\gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous coating layers, but instead only resulted in sparse patches of deposits on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker coating layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimization} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
\ds{
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between coating layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied. %to create a valley in between. 
This allowed material to only be deposited on the area between the tape.
After the coating layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous coating layers.
Thus, the \gls{db} speed was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization of \ch{ZrO2} Layers}
All characterization procedures were executed at room temperature.
\iffalse
%All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
%\td{5kV, raum temperature, vacuum???}
%
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). 
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
For transmittance the light entered the sample from the side with the coating layer. 
The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
%\td{
%
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
%. (where are the conditions?)}
All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.
\fi

@@

The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the \gls{zro} layer.

@@

Another measure is the density of shorted elements $\rho$ (pinhole ratio), calculated in following way:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-Optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e.\ my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

### 2024-08-11 doc/Thesis/chapter/04-computational-details.tex
nearly finish with todos from todo.md

\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e.\ experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e.\ conductivity, pinhole density, number of coated layers and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
\ref{sec:exp}, yielding the quantities 
$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
% and the responses conductivity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.

The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and 
again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
%the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

@@

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}

>>>>

\section{Evolutionary Model-Based Multiresponse Approach (EMMA)}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e.\ experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e.\ conductivity, pinhole ratio, number of coated layers and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
\ref{sec:exp}, yielding the quantities 
$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
% and the responses conductivity $\gamma$ (see eq. \ref{eq:gamma}), pinhole ratio $\rho_s$ (see eq. \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.

The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and 
again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
%the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and coating layer analysis.

@@

\section{Fitting Data via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
